Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-06 WSSSPE3/report/WSSSPE3_review.tex
Update with affiliation/email
minor change

\item How can we reduce systemic bias, which goes back to the blog post of
Dryden especially on how ethics of unpaid labor disproportionately affect
underrepresented communities?

>>>>

\item How can we reduce systemic bias, which goes back to Dryden's blog post
especially on how ethics of unpaid labor disproportionately affect
underrepresented communities?
